---
title: "p8105_hw3"
author: "Si Li"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r}
library(dplyr)
library(tidyverse)
```

Problem 1
```{r}
library(p8105.datasets)
data("instacart")
instacart %>% 
  summarise(n_aisle= n_distinct(aisle))

ais_n=
instacart %>% 
  count(aisle, name = "number")%>% 
  arrange(desc(number))

instacart %>% 
  count(aisle, name = "number")%>% 
  filter(number>10000)%>% 
  ggplot(aes(aisle, number, label=number))+
  geom_bar(stat="identity",position="dodge")+
  ggtitle("The number of times ordered in each aisle")+
  coord_flip()
  
instacart %>%
  count(aisle, name = "n_times") %>% 
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
  knitr::kable()
            
instacart %>% 
  group_by(product_name,order_dow) %>% 
  select(product_name, order_dow, order_hour_of_day) %>% 
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>%
  summarise(mean_order_hour=mean(order_hour_of_day)) %>% 
  mutate(order_dow = recode(order_dow, `0` ="Sun", `1` = "Mon", `2`= "Tues", `3`= "Wed", `4` = "Thurs", `5`= "Fri", `6`= "Sat")) %>% 
  pivot_wider(names_from = order_dow,
              values_from = mean_order_hour)%>% 
  knitr::kable()
```

The dataset have `r nrow(instacart)` rows and `r ncol(instacart)` columns. The number of aisles is `r summarise(instacart, n_aisle= n_distinct(aisle))`, the aisle that the most items ordered from is fresh vegetables. Some of the key variables are `r colnames(instacart[14:15])`. 

The most items are ordered from two aisles, fresh vegetables and fresh fruits, and the third one is packages vegetables fruits, meaning people are living more healthy these days. 

We can see from the table, among theses three aisles, packaged vegetables fruits has the biggest number of ordering times, followed by baking ingredients.

In Wednesday, Pink Lady Apples and Coffee Ice Cream have relatively the highest mean hour of the day. 

Problem 2
```{r}
library(p8105.datasets)
data("brfss_smart2010")
brfss=
brfss_smart2010 %>% 
  janitor::clean_names() %>% 
  filter(topic %in% "Overall Health") %>% 
  mutate(
    response= forcats::fct_relevel(response, c("Poor", "Fair", "Good", "Very good", "Excellent"))
    )
brfss

brfss%>% 
  filter(year=="2002") %>% 
  count(locationabbr, name="n_loc") %>% 
  mutate(n_loc= n_loc/5) %>%
  filter(n_loc>7)

brfss %>% 
  filter(year=="2010") %>% 
  count(locationabbr, name="n_loc") %>% 
  mutate(n_loc= n_loc/5) %>%
  filter(n_loc>7)

brfss %>% 
  filter(response=="Excellent") %>%
  group_by(year, locationabbr) %>% 
  summarise(ava_data=mean(data_value)) %>%
  ggplot(aes(x=year, y=ava_data))+
  geom_line(aes(group= locationabbr, color=locationabbr))+  
  ggtitle("Average data value for Excellent response among each state over years")

brfss %>% 
  filter(locationabbr=="NY" & year%in%c("2006","2010")) %>% 
  ggplot(aes(x=data_value , y=locationdesc, color=response))+
  geom_point()+
  facet_grid(~year)
```

In 2002, MA, NJ, PA states were observed at 7 or more locations; while in 2010, there are 11 states were observed at 7 or more locations.

The average data value for each state for response Excellent is quite steady over years.

In 2010, data value for very good is a little bet better than in 2006, besides, poor and fair response stay low in the data value.

Problem 3
```{r}
accel_data=
  read_csv(file = "./accel_data.csv") %>% 
  mutate(
    day=forcats::fct_relevel(day, c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))
    ) %>% 
  pivot_longer(
    activity.1:activity.1440,
    names_to = "activity",
    names_prefix = "activity.",
    values_to = "CHF"
  ) %>% 
  mutate(
    week_kind=case_when(
             day=="Saturday" ~ "weekend",
             day=="Sunday" ~ "weekend",
             TRUE ~ "weekday"
           )) %>%   
  select(week, week_kind, day, activity, CHF)

h_data=
  accel_data %>% 
  group_by(week, day) %>% 
  summarise(CHF_mean=mean(CHF, na.rm= TRUE)) 
h_data%>% 
  knitr::kable()

h_data %>% 
  group_by(week, day) %>% 
  ggplot(aes(x=week, y= CHF_mean, color= day)) +
  geom_line()
```

